Author Guidelines for DAGM-OAGM Submission

### 2013-09-19 intro.tex
Joe's corrections :)

\citet{nowozin2010parameter} provide a detailed evaluation of different aspects
of learning object class segmentation, that is somewhat orthogonal to this
work. Their work considers the choice of features, number superpixels and
pairwise potentials for conditional maximum likelihood learning of
tree-structured CRFs.  \citet{nowozin2010parameter} also compare conditional
maximum likelihood learning with maximum margin learning, finding little
difference in accuracy.
We focus our work on the more popular neighborhood graphs, which do not allow
for efficient inference.  Therefore, conditional maximum likelihood learning is
intractable in our setting. For our studies, we fix the considered feature set,
and vary the maximum margin learning algorithm. Despite this seemingly limited
setup, we can make out large differences in the applicability of some of the
commonly used methods. For comparison, we also evaluate the learning algorithms
on chain CRFs, where efficient inference is possible.
More recently, \citet{lucchi2013learning} proposed a novel algorithm for
efficiently learning structured prediction for semantic segmentation, using
approximate inference. In Chapter~\ref{ch:exact_learning}, we introduce an
algorithm that runs in similar time to the one proposed by
\citet{lucchi2013learning}, but is able to learn a CRF to the exact optimum on
the same dataset.

>>>>

\citet{nowozin2010parameter} provide a detailed evaluation of different aspects
of learning object class segmentation, that is somewhat orthogonal to this
work. Their work considers the choice of features, number of superpixels and
pairwise potentials for conditional maximum likelihood learning of
tree-structured CRFs.  \citet{nowozin2010parameter} also compare conditional
maximum likelihood learning with maximum margin learning, finding little
difference in accuracy.
We focus our work on the more popular neighborhood graphs, which do not allow
for efficient inference.  Therefore, conditional maximum likelihood learning is
intractable in our setting. For our studies, we fix the considered feature set,
and vary the maximum margin learning algorithm. Despite this seemingly limited
setup, we can make out large differences in the applicability of some of the
commonly used methods. For comparison, we also evaluate the learning algorithms
on chain CRFs, where efficient inference is possible.
More recently, \citet{lucchi2013learning} proposed a novel algorithm for
efficiently learning structured prediction for semantic segmentation, using
approximate inference. In Chapter~\ref{ch:exact_learning}, we introduce an
algorithm that runs in similar time to the one proposed by
\citet{lucchi2013learning}, but is able to learn a CRF to the exact optimum on
the same dataset.

### 2013-09-19 itm/paper.tex
Joe's corrections :)

Before we start our investigation of semantic segmentation and object class segmentation,
we look into a general purpose clustering algorithm.
%
In clustering, the goal is to divide data points into homogeneous subsets, called
clusters.
Many different formulations of the clustering problem are given in the literature.
%
In the context of this work, clustering plays an important role in many respects:
\begin{itemize}
    \item Clustering, as a purely unsupervised methods is on one end of the
        spectrum of algorithms we investigate.  When using per-image or
        per-pixel supervision as in the later chapters, we can use clustering
        to calibrate our expecation of what semisupervised and supervised
        algorithms should be able to achieve.

@@

    \item As many other computer vision algorithms, our segmentation methods
        depends on bag-of-feature representations of segments or images. These
        are build using a vocabulary of visual words that is usually created
        via clustering.
\end{itemize}

>>>>

Before we start our investigation of semantic segmentation and object class segmentation,
we look into a general purpose clustering algorithm.
%
In clustering, the goal is to divide data points into homogeneous subsets, called
clusters.
Many different formulations of the clustering problem are given in the literature.
%
In the context of this work, clustering plays an important role in many respects:
\begin{itemize}
    \item Clustering, as a purely unsupervised methods is on one end of the
        spectrum of algorithms we investigate.  When using per-image or
        per-pixel supervision as in the later chapters, we can use clustering
        to calibrate our expectation of what semi-supervised and supervised
        algorithms should be able to achieve.

@@

    \item As many other computer vision algorithms, our segmentation methods
        depends on bag-of-feature representations of segments or images. These
        are built using a vocabulary of visual words that is usually created
        via clustering.
\end{itemize}
